\chapter{Professional and Scientific Aspects}
\label{chap:professional}
\minitoc

\section{Courses}
The table~\ref{cursos} summarizes the courses followed during the PhD. project:
%\begin{itemize}
%\item \textit{Fran\c{c}ais pour non francophones niveau 1 beginner (2014-2015).} Code E. Transversal.
%\item \textit{Fran\c{c}ais pour non francophones niveau 1 beginner/d\'ebutant, \'el\'ementaire (2015-2016).} Code E. Transversal.
%\item \textit{Fran\c{c}ais pour non francophones niveau 2 interm\'ediaire (2015-2016).} Code E. Transversal.
%\item \textit{Writing a scientific paper step by step (2015-2016).} Code E. Transversal.
%\item \textit{E1a Fran\c{c}ais langue \'etrang\'ere-niveaux d\'ebutant \`a \'el\'ementaire - French as a Foreign language-beginner to elementary levels (2016-2017).} Code E. Transversal.
%\end{itemize}
\begin{table}[h!]
\center
\begin{tabular}{||c|p{8.5cm}|c|c||}
\hline 
\textbf{Code} & \textbf{Course} & \textbf{Hours} & \textbf{Year} \\ 
\hline \hline 
E1a & Fran\c{c}ais pour non francophones niveau 1 beginner & 39h & 2014 \\ 
\hline 
E1a & Fran\c{c}ais pour non francophones niveau 1 beginner/d\'ebutant, \'el\'ementaire & 39h & 2015 \\ 
\hline 
E1b & Fran\c{c}ais pour non francophones niveau 2 interm\'ediaire & 39h & 2015 \\ 
\hline 
E7 & Writing a scientific paper step by step & 20h & 2015 \\ 
\hline 
E1a & E1a Fran\c{c}ais langue \'etrangère-niveaux d\'ebutant \`a \'el\'ementaire - French as a Foreign language-beginner to elementary levels & 39h & 2016 \\ 
\hline 
\end{tabular}\caption{Attended courses.}\label{cursos} 
\end{table}

\section{Scientific production}

\noindent
\underline{D. A. S. Carvalho}, Nadia Bennani, Genoveva Vargas-Solar, Chirine Ghedira, Placido Souza Neto. \textbf{Can Data Integration Quality be Enhanced on Multi-cloud using SLA?}. DEXA 2015, Sep 2015, Valencia, Spain. Lecture Notes in Computer Science 9262, Springer 2015, pp. 145-152. [Rank: B -- Source: Core2014]

\bigskip
\noindent
M. A. Macedo, \underline{D. A. S. Carvalho}, M. A. Musicante, A. Pardo and U. S. Costa. \textbf{An abstract machine for integrating heterogeneous web applications}, 2015 IEEE/ACS 12th International Conference of Computer Systems and Applications (AICCSA), Marrakech, 2015, pp. 1-8. [Rank: C -- Source: Core2014]

\bigskip
\noindent 
\underline{D. A. S. Carvalho}, P. A. Souza Neto, G. Vargas-Solar, N. Bennani, C. Ghedira. \textbf{Rhone: a quality-based
query rewriting algorithm for data integration}, Short paper, 20th East-European Conference on Advances
in Databases and Information Systems, ADBIS 2016, pp. 80-87. [Rank: B -- Source: Core2014]

\bigskip
\noindent 
\underline{D. A. S. Carvalho}, P. A. Souza Neto, G. Vargas-Solar, N. Bennani, C. Ghedira. 
\textbf{Towards Quality Guided Data Integration on Multi-Cloud Settings},
Service-Oriented Computing - 14th International Conference, ICSOC 2016, PhD Symposium, Banff, AB, Canada, October 10-13, 2016. [Rank: A -- Source: Core2014]

\section{Other Dissemination Activities}

Dissemination activities are listed below. Among the others, the possibility \textit{(i)} to present regularly inside the research team and also in an external team; \textit{(ii)} to have regular meetings with the supervisors in order to show progress, discuss about technical and scientific issues, and formalization exercises; and \textit{(iii)} to prepare experimentation environments learning new technology are part of our work methodology. 

\subsection{Attending thematic schools}

\noindent
Participating on to the \textbf{1st French Brazilian School on Smart cities and Big Data} at the
University of Grenoble Alpes (http://fr-br-school.imag.fr). April 2015.

\subsection{Attending conferences as author}
\noindent
Paper presentation. \textbf{Rhone: a quality-based query rewriting algorithm for data integration} at the 20th East-European Conference on Advances in Databases and Information Systems, ADBIS 2016.

\subsection{Presentation in the Magellan's Research Center}
\noindent
Paper proposal presentation. \textbf{Trusted SLA-Guided Data Integration on Multi-cloud Environments}. Seminar presented to the Information System group from the Magellan's Research Center. In March 5th 2015.

\bigskip
\noindent
Query rewriting algorithm and ongoing works presentation. \textbf{A Service-based Query Rewriting Algorithm}. to the Information System group from the Magellan's Research Center. In 4th February 2016.

\subsection{External presentation}
\noindent
PhD proposal and query rewriting algorithm presentation. \textbf{Trusted SLA-Guided Data Integration on Multi-cloud Environments}. Seminar presented to the Service-Oriented Computing team meeting from LIRIS, Lyon 1. In 3rd December 2015.

\bigskip
\noindent
Seminar concerning the paper accepted to the ADBIS 2016. \textbf{Rhone: a quality-based query rewriting algorithm for data integration}. Presented to the Information System group from the Magellan's Research Center. In September 22th 2016.

\subsection{Presentation in ARC 6 scientific manifestations}

\noindent
Poster presentation. \textbf{SLA-Guided Data Integration on Multi-cloud Environments}. Poster presented in the << Journ\'ee Scientifique de l'Arc 6 >> held in 20th November 2015 at Grenoble, France. 

\bigskip
\noindent
Poster presentation. \textbf{SLA-Guided Data Integration on Multi-cloud Environments}. Poster presented in the << Journ\'ee Scientifique de l'Arc 6 >> held in 24th November 2016 at Lyon, France.