\documentclass{llncs}
\usepackage{graphicx,color}
\usepackage{xspace}
\usepackage{amssymb} 
\usepackage{epstopdf}
\usepackage{algorithm} 
\usepackage{algorithmic}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multibib} 
\usepackage{datatool}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.10}  
\usetikzlibrary{patterns}
\usepackage{lscape} 
\usepackage{subfig}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage[thmmarks,amsmath]{ntheorem}

\newcommand{\openbox}{\leavevmode
  \hbox to.77778em{%
  \hfil\vrule
  \vbox to.675em{\hrule width.6em\vfil\hrule}%
  \vrule\hfil}}

\theoremstyle{plain}
\theoremheaderfont{\normalfont\bfseries}
\theorembodyfont{\normalfont}
\theoremseparator{}
\theoremindent0cm
\theoremnumbering{arabic}
\newtheorem{algo}{Algorithm}

\theoremstyle{plain}
\theoremheaderfont{\normalfont\bfseries}
\theorembodyfont{\normalfont}
\theoremseparator{}
\theoremindent0cm
\theoremnumbering{arabic}
\theoremsymbol{\ensuremath{\openbox}} 


\theoremstyle{plain}
\theoremheaderfont{\normalfont\bfseries}
\theorembodyfont{\normalfont}
\theoremseparator{.}
\theoremindent0cm
\theoremnumbering{arabic}
\theoremsymbol{\ensuremath{\Box}} 
\newtheorem{defi}{Definition}

\theoremstyle{plain} 
\theoremsymbol{\ensuremath{\Box}} 
\theoremseparator{.} 
\newtheorem{prop}{Property}

\def\FlyingPig{\textsl{FlyingPig}}

\newcounter{numberInTrivlist}

\newenvironment{numtrivlist}{\begin{list}{\rm \arabic{numberInTrivlist})} 
                                         {\usecounter{numberInTrivlist}
                                          \setlength{\leftmargin}{0pt}
                                          \setlength{\rightmargin}{0pt}
                                          \setlength{\itemindent}{12pt}
                                          \setlength{\listparindent}{0pt}}}
                            {\end{list}}

\newenvironment{itemizedTrivlist}{\begin{list}{\rm ~\hspace{2mm} $\bullet$\ } 
                                         {\setlength{\leftmargin}{0pt}
                                          \setlength{\rightmargin}{0pt}
                                          \setlength{\itemindent}{12pt}
                                          \setlength{\listparindent}{0pt}}}
                            {\end{list}}

\usepackage{listings}


\lstset{numbers=right, numbersep=5pt, numberstyle=\tiny, stepnumber=1,escapechar=\!,columns=fullflexible,
        morekeywords={procedure,let,for,do,if,then,else,add,choose,end,while,
        true,false,rise,exception,extend,resume,to,return,function}}

\newcommand{\pisodm}[0]{$\pi$SOD-M\xspace}


\newcommand \tqI[1]{\hbox{${\cal T}_{\mathrm{init}} [\![\ #1\ ]\!]$}}
\newcommand \tqT[1]{\hbox{${\cal T}_{\mathrm{cond}} [\![\ #1\ ]\!]$}}
\newcommand \tqS[1]{\hbox{${\cal T}_{\mathrm{inc}} [\![\ #1\ ]\!]$}}
\newcommand \agg[1]{\ensuremath{{\cal A}{gg}(#1)}}


\def\P{\hbox{${\cal P}$}}
\def\bigLS{\hbox{${\cal L_{S}}$}}
\def\bigLCSD{\hbox{${\cal L_{CSD}}$}}
\def\bigS{\hbox{${\cal S}$}}
\def\bigV{\hbox{${\cal S}$}}
\def\V{\hbox{${S}$}}
\def\v{\hbox{${s}$}}
\def\MCDws{\ifmmode \mathit{COR\_D}\else \textit{COR\_D}\fi}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\begin{document}
 
% ------ title and authors ----- % 

\title{\textit{Rhone}: a quality-based query rewriting algorithm for data
integration.}
\author{Daniel A. S. Carvalho\inst{1} \and Pl\'acido
		A. Souza Neto\inst{2} \and Chirine Ghedira-Guegan\inst{3} 
		\and Nadia Bennani\inst{4} \and Genoveva Vargas-Solar\inst{5} }
 
\institute{ 
Universit\'e Jean Moulin Lyon 3, Centre de Recherche Magellan, IAE, France\\
\email{daniel.carvalho@univ-lyon3.fr} \and
Instituto Federal do Rio Grande do Norte - IFRN, Natal, Brazil\\
\email{placido.neto@ifrn.edu.br} \and
Universit\'e de Lyon, CNRS, IAE - Universit\'e Lyon 3, LIRIS, UMR5205, France\\
\email{chirine.ghedira-guegan@univ-lyon3.fr} \and
LIRIS, INSA-Lyon, France\\
\email{nadia.bennani@insa-lyon.fr} \and
CNRS-LIG, Grenoble, France\\
\email{genoveva.vargas@imag	.fr} 
}

\maketitle

% ------ enf of title and authors ----- %
  
% ------ abstract and keywords ----- %
\begin{abstract}
Nowadays, data provision is mostly done by data services. Data integration can
be seen as composition of data services and data processing services that can
deal with to integrate data collections. With the advent of cloud, producing service compositions is
computationally costly. Furthermore, executing them can require a considerable
amount of memory, storage and computing resources that can be provided by
clouds. Our research focuses on how to enhance the results on the increase of cost on data integration in the new context of cloud.
To do so, we present in this paper our original data integration approach which takes into account user's
integration requirements while producing and delivering the results. The
service selection and service composition are guided by the service level
agreement - SLA exported by different services (from one or more clouds) and used by our matching algorithm (called \textit{Rhone}) that addresses the query rewriting for data integration presented here as proof of concept.
\end{abstract}
 
\keywords{Data integration. Query rewriting. Query rewriting algorithm. Cloud computing. SLA.}
 
% ------ end of abstract and keywords ----- %

\section{Introduction}\label{sec:introduction}
\input{introduction}
\section{Related works}\label{sec:relatedwork}
\input{related-works}
\section{Rhone service-based query rewriting algorithm}\label{sec:rhone}
\input{rhone-description}
\input{rhone-formalization}
\section{Evaluation}\label{sec:experiments}
\input{rhone-experiments}
\section{Final Remarks and Future Works}\label{sec:conclusion}
\input{conclusion}

\bibliographystyle{splncs03} 
\bibliography{bibliography}
\end{document}