Related works rely on four topics: 
(\textit{i}) data integration and data quality in the database domain;
(\textit{ii}) data integration approaches in the cloud and in service-oriented contexts; 
(\textit{iii}) query rewriting approaches; and 
(\textit{iv}) service level agreements for cloud computing.

Data integration has been widely discussed in the database domain.
\cite{Lenzerini:2002} discussed theoretical aspects in data integration including modeling applications, query evaluation, dealing with inconsistencies and reasoning queries.
Moreover, \cite{Halevy:2001} reviewed several query rewriting approaches. 
\cite{Batini2006} surveyed data quality aspects in data integration systems. 
\cite{Scannapieco:2004} presented a data quality broker that allows to submit queries with associated quality requirements over a global schema and to provide results according to them.

\cite{Correndo2010,ElSheikh2013} performed data integration in service-oriented contexts, particularly considering data services. However, they  consider computing resources consumption versus performance for guiding the data integration process. 
%\cite{YauY08} addressed data privacy  to integrate data collected from different data services. 
\cite{Tian2010} proposed an inter-cloud data integration system considering privacy requirements and the cost for protecting and processing data. 
\cite{Scannapieco:2004,Tian2010,YauY08} tackled quality aspects of the integration, but do not consider crucial aspects such as data consumers and data providers requirements and constraints, the associated infrastructures and the data quality itself. %It is also important to include these criteria in the way services are composed to produce  query plans.

As traditional databases theory, data integration on cloud and service-oriented context deals with query rewriting issues. Existing works like~\cite{ba2014,Barhamgi2010,Benouaret2011,Umberto} have refered it as a service composition problem. Given a query, the objective is to lookup and compose data services that can contribute to produce a result. In general, these works must address performance issues, because they use algorithms that can become expensive according to the complexity of the query and on the number of available services. Although \cite{ba2014,Benouaret2011} have considered preferences and scores to produce rewritings, the multi-cloud context introduces new requirements and constraints to the integration process. Currently, the approaches are not sufficient to cover the new challenges. Thus, they should be revisited and adapted in order to make the integration efficient in this new environment. 

%Service level agreements (SLA) have been widely adopted in different domains to specify what service consumer can expect from the service delivered by a service provider. 
Research contributions related to SLA in cloud computing concern (i) SLA management; (ii) inclusion of security requirements on SLAs; (iii) SLA negotiation; (iv) SLA matching; and (v) monitoring and allocation of cloud resources to detect and avoid SLA violations. 
%Research contributions in cloud computing mainly concern (i) SLA negotiation phase (step in which the contracts are established between customers and providers) and (ii) monitoring and allocation of cloud resources to detect and avoid SLA violations.
We strongly believe that SLAs can be used  to explicitely introduce the notion of quality in the current data integration solutions. In this sense, the use of SLAs to guide the entire data integration in a multi-cloud context seems original and promising for providing new perspectives to the data integration problem.
